Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-05-16 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
complete draft of intro, methods section; corrections to parameter space graphic

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$. \hl{Why heating frequency difficult? Need for modeling.}

@@

	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s from filtered SDO/AIA \citep{pesnell_solar_2012,lemen_atmospheric_2012} 94 \ang images of AR cores using an event detection algorithm. \hl{Steady-heating counter arguments?}

@@

	\par\hl{Heating frequency and emssion $T>T_m$}

@@

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes. We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

>>>>

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.

@@

	\par The frequency of energy release in the solar corona is an important piece of evidence for determining the yet unknown coronal heating mechanism(s). However, measurement of the heating frequency, through both direct and indirect means, has proved challenging. With regard to the direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a supposed precursor to bursty energy release. Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing these $\mathrm{EM}$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}. Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.

@@

	\par Hydrodynamic loop models, combined with sophisticated forward modeling, provide an accurate method for assessing a wide variety of heating scenarios and calculating observables. Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. 

@@

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. We now turn our attention to repeated impulsive events on a single strand.
	\par In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting $\mathrm{EM}(T)$. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions, with events drawn from a power-law distribution versus uniform heating rates. Additionally, we investigate the effect of scaling the inter-event waiting time to the event energy and as well as how NEI may affect the presence of hot emission. We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014}, to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.
